MSGenova (Clean version) Rmakrdown Report

### 2022-09-13 script/ms_report.Rmd
update advanced_config file, update Genotype_vcf rule, add comments to rules

```{r load_library, echo=FALSE, warning=FALSE, error=FALSE}
library(tidyverse)
library(DT)
library(ggplot2)
library(plyr)
library(dplyr)
library(shiny)
vector_calling<-params$vector
run_chromomap<-FALSE
DP.min<-params$DP.min
AR.min<-params$AR.min
workspace<-params$result_dir
sample_sheet<-params$sample
trimmo<- params$trimmo
flagstat<- params$flagstat
haplotype_caller<- params$haplotype_caller
setwd(workspace)
```

>>>>

```{r load_library, echo=FALSE, warning=FALSE, error=FALSE}
library(tidyverse)
library(DT)
library(ggplot2)
library(plyr)
library(dplyr)
vector_calling<-params$vector
run_chromomap<-FALSE
DP.min<-params$DP.min
AR.min<-params$AR.min
workspace<-params$result_dir
sample_sheet<-params$sample
trimmo<- params$trimmo
flagstat<- params$flagstat
haplotype_caller<- params$haplotype_caller
setwd(workspace)
```
